Experiments

### 2021-01-29 StateOfPractice/Methodology/Experiments.tex
added isability intro

~\newpage
\section{User Experiments}
\subsection{Usability Experimental Procedure}

>>>>

~\newpage
\section{User Experiments}
\subsection{Usability Experimental Procedure}
The purpose of this experiment is to assess the usability of each software package and collect qualitative data. An initial step is required to define a set of tasks for the experiment. The guideline below would assist domain experts in defining a list usability tasks for each domain.
This list will then be used to evaluate the usability of each selected software package. It is expected that the list would allow experimenters perform tasks in  different aspects of the software package and provide their evaluation using a standardized usability questionnaire ( \url{https://www.usabilitest.com/sus-pdf-generator}- 20-29 , \url{https://uiuxtrend.com/pssuq-post-study-system-usability-questionnaire/} - PSSUQ) - (we need to decide on the questionnaire to use eventually)
